Exploring probability distributions for bivariate temporal granularities

### 2019-10-29 main.Rmd
relating linear granularity with circular one

A linear granularity, as defined by [@Bettini1998-ed], is essentially a mapping of the index set to subsets of the bottom granularity. For example, if the bottom granularity is days, then a linear granularity might be weeks, months or years. Here, the domain is the index set and range is subsets of bottom granularity. Circular granularity, joining two linear granularities, therefore is a mapping between these two subsets of bottom granularity. They also accomodate periodicity and hence the smaller subsets of bottom granularity are nested within the larger subsets of bottom granularity. We use modular arithmetic to define circular granularity and use the following definitions:

>>>>

A linear granularity, as defined by [@Bettini1998-ed], is essentially a mapping of the index set to subsets of the bottom granularity. Here, the domain is the index set and range is subsets of bottom granularity. Circular granularity, joining two linear granularities, therefore is a mapping between these two subsets of bottom granularity. They also accomodate periodicity and hence the smaller subsets of bottom granularity are repeating themselves within the larger subsets of bottom granularity. We use modular arithmetic to define circular granularity and use the following definitions:
